Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-05-26 props.tex
Back to the "join" version.

@@

    We define policy-sensitive observational equivalence, which relates machine traces and
    {\it mptraces} whose observable behavior match up to a possible halt due to policy failure.
    It relates lists of parameters as long as only the last is infinite.

@@

    \[\frac{\begin{split}
              \MP \not \in \top & \hspace{.5cm} M \not \in \top \\
              \mathit{Obs}(\MP) \simeq \mathit{Obs}(M) & \hspace{.5cm} \overline{\MP} \sim_P \overline{M} \\
            \end{split}}
           {\MP \overline{\MP} \sim_P M \overline{M}}\]

@@

              \((m_r,p_r) \hookrightarrow \MP_2\), and \(m_r'' \hookrightarrow M_2'\)
            \item \(\MP_1 \MP_2 \sim_P M_1' M_2'\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\),
          \(\MP \sim_P M'\)
      \end{itemize}

>>>>

    When we've taken a prefix and want to combine it with another trace by replacing its final
    state and continuing execution, we use the join operator on any type of trace \(T_1 \cdot T_2 :
    \mathit{trace}\ X \rightarrow \mathit{trace}\ X \rightharpoonup \mathit{trace}\ X\), defined
    on \(T_1 \not \in \top\) and any \(T_2\):

    \[T_1 \cdot T_2 \triangleq
      \begin{cases}
        T_2 & \text{if } T_1 = t \\
        t T_1' \cdot T_2 & \text{if } T_1 = t T_1' \\
      \end{cases}\]

@@

    We define policy-sensitive observational equivalence, which relates a machine trace and
    an {\it mptrace} whose observable behavior match, up to a possible halt due to policy failure.

@@

@@

              \((m_r,p_r) \hookrightarrow \MP_2\), and \(m_r'' \hookrightarrow M_2'\)
            \item \(\MP_1 \cdot \MP_2 \sim_P M_1' \cdot M_2'\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\),
          \(\MP \sim_P M'\)
      \end{itemize}
